### 2016-08-31 version0.0/summary.tex
Applying P.W.'s comments on adding the big picture to the summary

%future works and add big questions
To move forward, we would like to test star formation laws in high-redshift galaxies with the hierarchical Bayesian regression fitting method. This would allow investigation of both the effects of fitting methods on using global values for galaxies and differences in using this method on nearby galaxies and high-redshift ones.  
We could also use data mining methods to recalibrate the correlations between luminosities from star forming regions and the SFR in both nearby and high redshift galaxies.
Self-organizing maps can help us to examine our calibrations of the SFR, find their flaws and predict the SFR in distant galaxies.
Another project to continue after this thesis would be to show that self-organizing maps are good tools to predict properties of galaxies and estimate values of unobserved quantities.
Continuing the work in Chapter~\ref{ch: paper3}, we would like to obtain mid-infrared spectroscopy with more coverage in M31 and other nearby galaxies to have a higher dimensional sample for creating SOMs as well as to investigate the anti-correlation between stellar mass and PAHs.
Having these new calibrations for finding properties of galaxies and applying them to observations from recently (or soon to be) operational telescopes such as TMT, ALMA, SKA, and {\it JWST} would help us solve the mystery of how stars form and evolve in time.

>>>>

%future works and add big questions
In this thesis we first measured star formation rate in a nearby galaxy and tested the the current star formation laws using Bayesian statistic on the galaxy.
We used data mining methods study  observed or measured quantities of the nearby galaxies and compare them with the SFR.
We then applied the spectra of high-redshift galaxies to determine the correlation between SFR with properties of galaxies in a distant galaxies and through the time.
To move forward, we would like to test star formation laws in high-redshift galaxies with the hierarchical Bayesian regression fitting method. This would allow investigation of both the effects of fitting methods on using global values for galaxies and differences in using this method on nearby galaxies and high-redshift ones.  
We could also use data mining methods to recalibrate the correlations between luminosities from star forming regions and the SFR in both nearby and high redshift galaxies.
Self-organizing maps can help us to examine our calibrations of the SFR, find their flaws and predict the SFR in distant galaxies.
Another project to continue after this thesis would be to show that self-organizing maps are good tools to predict properties of galaxies and estimate values of unobserved quantities.
Continuing the work in Chapter~\ref{ch: paper3}, we would like to obtain mid-infrared spectroscopy with more coverage in M31 and other nearby galaxies to have a higher dimensional sample for creating SOMs as well as to investigate the anti-correlation between stellar mass and PAHs.
Having these new calibrations for finding properties of galaxies and applying them to observations from recently (or soon to be) operational telescopes such as TMT, ALMA, SKA, and {\it JWST} would help us solve the mystery of how stars form and evolve in time.
